---
title: "Favorite foods"
author: "Fiona Wang"
date: "`r Sys.Date()`"
output: 
  html_document: 
    toc: yes
    toc_float: yes
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(readxl)
library(forcats)
```

# Part 1: Excel to CSV Workflow


## Step 1: Read the Data

* Read in the Excel file called `favourite-food.xlsx` from the `data-raw/` folder.

```{r read_excel, eval=FALSE}
fav_food <- read_excel(path = "data-raw/favourite-food.xlsx")
fav_food
```

## Step 2: Clean the Data

* Clean up the missing data (`NA`s) and make sure you're happy with variable types. Modify the `read_excel` function to take care of these issues.

```{r clean, eval=FALSE, warning =FALSE}
fav_food <- read_excel(
  path = "data-raw/favourite-food.xlsx",
  na = c("", "N/A", "99999"))
fav_food <- fav_food %>% 
  mutate(AGE = case_when(
    AGE == "five" ~ 5,
    TRUE ~ as.numeric(AGE)
  ))
fav_food 
```

* Convert the SES (socioeconomic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r SES_factor}
fav_food <- fav_food %>% 
  mutate(SES = factor(SES, levels = c("Low", "Middle", "High")))

# add code here
```

## Step 3: Save to CSV

* Write out the resulting data frame to `favourite-food.csv` in the `data/` folder.

```{r Save_CSV}
write_csv(fav_food, file = "data-raw/favourite-food.csv")
# add code here
```

## Step 5: Verify CSV Data

* Finally, read `favourite-food.csv` back in from the `data/` folder and 
observe the variable types. Are they as you left them?

```{r check_csv}
fav_food_check <- read.csv("data-raw/favourite-food.csv")
# add code here
```

# Part 2: Excel to RDS Workflow

## Step 1: Read the Data
* Similar to Part 1, read  the Excel file called `favourite-food.xlsx` from the `data-raw/` folder, and handle missing data and variable types.

```{r read_xlsx, eval=FALSE, warning = FALSE}
fav_food2 <- read_excel(path = "data-raw/favourite-food.xlsx",
                       na = c("", "99999", "N/A"))
fav_food2 <- fav_food2 %>% 
  mutate(AGE = case_when(
                         AGE == "five" ~ 5,
                         TRUE ~ as.numeric(AGE)
                       ))
                       
fav_food2 
str(fav_food2)
```

## Step 2: Adjust Variable Types

* Convert SES (socioeconomic status) to a factor variables with levels in the 
following order: `Low`, `Middle`, `High`.

```{r SES_convert}
fav_food2 <- fav_food2 %>% 
  mutate(SES = factor(SES, levels = c("Low", "Middle", "High")))
str(fav_food2)
fav_food3 <- fav_food2 %>% 
  mutate(SES_numeric = as.numeric(SES))
# add code here
```

## Step 3: Save to RDS
* Write out the resulting data frame to `favourite-food.rds` in the `data/` folder.

```{r save_RDS}
write_rds(fav_food3, file = "data-raw/favourite-food.rds")
# add code here
```

* Read `favourite-food.rds` back in from the `data/` folder and observe the 
variable types. Are they as you left them?

```{r check_RDS}
fav_food3_check = read_rds("data-raw/favourite-food.rds")
# add code here
```

## References {#references}
1. Assignment Adapted from [Mine Cetinkaya-Rundel's Data Science in a Box](https://github.com/rstudio-education/datascience-box)